Satellite Alignments in Galaxy Pairs

### 2016-05-23 paper/ms.tex
general sample

General Pair Sample.

>>>>

We select all halos with maximum circular velocities in the
range 150 km s$^{-1}$ $<V_{\rm max}<$ 350 km s$^{1}$.
We exclude sub-halos from this selection.
From this set we construct a sample of pairs as follows.
For each halo $A$ we find its closest halo $B$, if halo $A$ is also
the closest to halo $B$, the two halos are considered as a pair. 
Another way to phrase this selection is that pairs do not have
neighbors closer than the pair's distance.
There are $53$ pairs with those conditions in the simulation.

We extract from the simulation spheres of $2$
